### 2009-03-25 doc/storage_system/arc-storage-manual.tex
added gateway to manual and a small change in the documentation

\documentclass{book}
\usepackage{graphicx}                              %for PNG images (pdflatex)
\usepackage[linkbordercolor={1.0 1.0 0.0}]{hyperref} %for \url tag
\usepackage{color}                                 %for defining custom colors
\usepackage{framed}                                %for shaded and framed paragraphs
\usepackage{textcomp}                              %for various symbols, e.g. Registered Mark
\usepackage{geometry}                              %for defining page size
\usepackage{longtable}                             %for breaking tables
%
\geometry{verbose,a4paper,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2cm}
\hypersetup{
  pdfauthor = {Zsombor Nagy},
  pdftitle = {User's manual of the ARC storage system},
  pdfsubject = {Paper subject},
  pdfkeywords = {Paper,keyword,comma-separated},
  pdfcreator = {PDFLaTeX with hyperref package},
  pdfproducer = {PDFLaTeX}
}
%
\bibliographystyle{IEEEtran}                       %a nice bibliography style
%
\def\efill{\hfill\nopagebreak}%
\hyphenation{Nordu-Grid}
\setlength{\parindent}{0cm}
\setlength{\FrameRule}{1pt}
\setlength{\FrameSep}{8pt}
\addtolength{\parskip}{5pt}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand{\arraystretch}{1.3}
\newcommand{\dothis}{\colorbox{shadecolor}}
\newcommand{\ngdl}{\url{http://ftp.nordugrid.org/download}~}
\definecolor{shadecolor}{rgb}{1,1,0.6}
\definecolor{salmon}{rgb}{1,0.9,1}
\definecolor{bordeaux}{rgb}{0.75,0.,0.}
\definecolor{cyan}{rgb}{0,1,1}
%
%----- DON'T CHANGE HEADER MATTER
\hyphenation{preserve-Original}
\begin{document}
\def\today{\number\day/\number\month/\number\year}

@@

%%%%---- The title ----
{\centering \textsc{\Large Administrator's and user's manual of the ARC storage system}\Large \par}
\vspace*{0.5cm}

@@

>>>>

\documentclass{book}
\usepackage{graphicx}                              %for PNG images (pdflatex)
\usepackage[linkbordercolor={1.0 1.0 0.0}]{hyperref} %for \url tag
\usepackage{color}                                 %for defining custom colors
\usepackage{framed}                                %for shaded and framed paragraphs
\usepackage{textcomp}                              %for various symbols, e.g. Registered Mark
\usepackage{geometry}                              %for defining page size
\usepackage{longtable}                             %for breaking tables
%
\geometry{verbose,a4paper,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2cm}
\hypersetup{
  pdfauthor = {Zsombor Nagy},
  pdftitle = {Administrator's manual of the ARC storage system},
  pdfsubject = {Paper subject},
  pdfkeywords = {Paper,keyword,comma-separated},
  pdfcreator = {PDFLaTeX with hyperref package},
  pdfproducer = {PDFLaTeX}
}
%
\bibliographystyle{IEEEtran}                       %a nice bibliography style
%
\def\efill{\hfill\nopagebreak}%
\hyphenation{Nordu-Grid}
\setlength{\parindent}{0cm}
\setlength{\FrameRule}{1pt}
\setlength{\FrameSep}{8pt}
\addtolength{\parskip}{5pt}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand{\arraystretch}{1.3}
\newcommand{\dothis}{\colorbox{shadecolor}}
\newcommand{\ngdl}{\url{http://ftp.nordugrid.org/download}~}
\definecolor{shadecolor}{rgb}{1,1,0.6}
\definecolor{salmon}{rgb}{1,0.9,1}
\definecolor{bordeaux}{rgb}{0.75,0.,0.}
\definecolor{cyan}{rgb}{0,1,1}
%
%----- DON'T CHANGE HEADER MATTER
\hyphenation{preserve-Original}
\begin{document}
\def\today{\number\day/\number\month/\number\year}

@@

%%%%---- The title ----
{\centering \textsc{\Large Administrator's manual of the ARC storage system}\Large \par}
\vspace*{0.5cm}

@@

\section{Accessing external storage solutions} % (fold)
\label{sec:using_the_gateway}

If we have permissions to access some third-party storage solutions (e.g. dCache), we can create a mount point within the namespace of the ARC storage system which points to a third-party URL, and then we can use the client interface of the ARC storage to access the third-party storage as well. This is achieved by a module of the Bartender, called the `Gateway'. Currently only GridFTP access is supported, and for that we need to install the Globus libraries to our machines. Then we need to recompile our source for GridFTP support. The output of the \verb!configure! script should look like this:

\begin{verbatim}
    Available third-party features:

    RLS:                yes
    GridFTP:            yes
    LFC:                no
    RSL:                yes
    SAML:               yes
    MYSQL CLIENT LIB:   no
    gSOAP:              yes

    Included components:
    A-Rex service:      no
    ISI service:        no
    CHARON service:     no
    HOPI service:       yes
    SCHED service:      no
    STORAGE service:    yes
    PAUL service:       no
    SRM client (DMC):   yes
    GSI channel (MCC):  yes
\end{verbatim}

After compilation and installation we can use the \verb!arcls! tool to list the content of a third-party storage. Let's check if our Billy user has access to this directory:

\begin{verbatim}
$ arcls gsiftp://sal1.uppmax.uu.se:2811/pnfs/uppmax.uu.se/data
data1
data2
other
\end{verbatim}

We can see some files in there, so we have permissions to list that directory.

Now let's configure the Bartenders on all three machines to use the Gateway module:

\begin{verbatim}
<Service name="pythonservice" id="bartender">
    <ClassName>storage.bartender.bartender.BartenderService</ClassName>
    <LibrarianURL>[...]</LibrarianURL>
    <ProxyStore>/var/spool/arc/proxy_store</ProxyStore>
    <GatewayClass>storage.bartender.gateway.gateway.Gateway</GatewayClass>
    <GatewayCfg>
        <ProxyStore>/var/spool/arc/proxy_store</ProxyStore>
        <CACertificatesDir>/etc/grid-security/certificates</CACertificatesDir>
    </GatewayCfg>
    <ClientSSLConfig FromFile="/etc/arc/clientsslconfig.xml" />
</Service>
\end{verbatim}

Let's start all three servers. Then create a mount point with the Logical Name \verb!/salmount! which points to this URL:

\begin{verbatim}
$ arc_storage_cli makemount /salmount \
    gsiftp://sal1.uppmax.uu.se:2811/pnfs/uppmax.uu.se/data
- Calling the Bartender's makeMountpoint method...
- done in 3.07 seconds.
Creating mountpoint '/salmount': done

$ arc_storage_cli stat /salmount
- Calling the Bartender's stat method...
- done in 0.47 seconds.
'/salmount': found
  states
    closed: 0
  entry
    owner: /DC=eu/DC=KnowARC/O=knowarc/CN=billy
    type: mountpoint
    GUID: b21d9d22-e885-502a-ee0e-bd0a7b967543
  parents
    0/salmount: parent
  mountpoint
    externalURL: gsiftp://sal1.uppmax.uu.se:2811/pnfs/uppmax.uu.se/data
  timestamps
    created: 1237990168.09
\end{verbatim}

Let's list the content of this mountpoint:

\begin{verbatim}
$ arc_storage_cli list /salmount- Calling the Bartender's list method...
- done in 0.49 seconds.
'/salmount': Your proxy cannot be found. Please delegate your credentials!
\end{verbatim}

Yes, we first need to delegate our credentials with the \verb!credentialsDelegation! method, then try to list the mount point:

\begin{verbatim}
$ arc_storage_cli cre
- Calling the Bartender's credentialsDelegation method...
[...]
- done in 0.42 seconds.
Successful delegation.
Proxy ID: eNCMDmi8i6YnPSAtDmVmuSEmABFKDmABFKDm0zKKDmFBFKDmeOzdBo

$ arc_storage_cli list /salmount
- Calling the Bartender's list method...
- done in 3.19 seconds.
'/salmount': collection
  data1  <unknown>
  data2  <unknown>
  other  <unknown>
\end{verbatim}

Let's download a file:

\begin{verbatim}
$ arc_storage_cli get /salmount/data1 /tmp
- Calling the Bartender's getFile method...
- done in 3.56 seconds.
- Got transfer URL: gsiftp://sal1.uppmax.uu.se:2811/pnfs/uppmax.uu.se/data/data1
- Downloading from 'gsiftp://sal1.uppmax.uu.se:2811/pnfs/uppmax.uu.se/data/data1'
    to '/tmp/data1' with gridftp...
   2 s:        0.0 kB       0.0 kB/s       0.0 kB/s    . . .       
   3 s:        1.3 kB       0.4 kB/s       0.4 kB/s    . . .       
- done in 2.7828 seconds.
'/salmount/data1' (1290 bytes) downloaded as '/tmp/data1'.
\end{verbatim}
